Dependent Object Types

### 2012-09-11 doc/candidacy/slides.tex
formatting

\begin{frame}[fragile]{``Translucent'' ML: Example}
\begin{minted}{sml}
structure XInt = struct
  type T = int
  val v = 3
  val f = negate
end
structure XBool = struct
  type T = bool
  val v = true
  val f = not
end
structure X =
  if flip() then XInt else XBool
signature XType = sig
  type T
  val v: T
  val f: T -> T
end
\end{minted}
\end{frame}

>>>>

\begin{frame}[fragile]{``Translucent'' ML: Example}
\begin{columns}
\begin{column}[t]{5cm}
\begin{minted}{sml}
structure XInt = struct
  type T = int
  val v = 3
  val f = negate
end
structure XBool = struct
  type T = bool
  val v = true
  val f = not
end

structure X =
  if flip() then XInt else XBool
\end{minted}
\end{column}
\begin{column}[t]{5cm}
\begin{minted}{sml}
signature XType = sig
  type T
  val v: T
  val f: T -> T
end
\end{minted}
\end{column}
\end{columns}
\end{frame}
